{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2022-01-11 main.tex
miscellaneous and unfinished parallelization
Push

	\subsection{Motivate Simulation for some data generating process from application}
	For the simulation study, we use the gasoline dataset to predict the octane ratings of gasoline samples relying on the introduced methods. This has become more relevant as modern internal combustion engines become more complex and rely on precisely tuned fuels. The dataset, which contains 60 i.i.d. observations with each 400 measurements, was constructed using Near infra-red (NIR) spectroscopy, which allows to analyse samples of gasoline much faster and with the same reproducibility as standard tests (cf. \cite{Bohacs_Ovadi_Salgo1998}). The study follows Reiss and Ogden (2007) as a guideline. Similar to Reiss and Ogden (2007), two different true coefficient functions $f_1$ and $f_2$ were chosen that differ in their smoothness:

	\begin{equation}
    	f_1 = 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t) 
    \end{equation}

    \begin{equation}
    	f_2 = 1.5^{\frac{-0.5(t-0.3)^2}{0.02^2}} - 4^{\frac{-0.5(t-0.45)^2}{0.015^2}} +  8^{\frac{-0.5(t-0.6)^2}{0.02^2}} -  1^{\frac{-0.5(t-0.8)^2}{0.03^2}}
    \end{equation}

Two different error-terms $\epsilon $ were created by first generating iid standard normal error and then multiplying them by $\sigma_e $ which is calculated such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6. The two error-terms are then computed to generate two sets of responses with different signal-to-noise ratios for each true function, using the gasoline dataset. These four combinations are then used with different number of basis-function $(5,6,...,25)$ of the order 5 to predict the responses using the b-spline basis approach and the FPCR approach. Within one repetition, the data is randomly sampled into a training and a test set to calculate the reported test MSE. The simulation was done with R (version...). In total we carried out 2000 simulations for each combination of data and number of basis functions. {\color{green} Information about version and link to repo / package in footnote??}

	\subsection{Generating Similar Curves}
    {\color{blue} I shifted this from theory to over here, as it makes more sense in the simulation part.\\
    Very short summary: take fpc's and eigenvalues, use that the scores are independent from each other. Use the eigenvalues as variances and draw from a multivariate normal with the right varcov matrix (normal just because of convenience... No theoretical reasoning)}
	\subsection{Results}

>>>>

	\subsection{Motivation}
	For the simulation study, we deviate from the standart simulation setting. Instead of generating data by ourself, we use the data from the gasoline dataset ($NIR$) to predict the octane ratings of gasoline samples, relying on the introduced methods. The dataset, which contains 60 i.i.d. observations with each 400 measurements, was constructed using Near infra-red (NIR) spectroscopy, which allows to analyse samples of gasoline much faster and with the same reproducibility as standard tests (cf. \cite{Bohacs_Ovadi_Salgo1998}).

	\subsection{Generating Similar Curves}
	To avoid small sample problems, we generated similar curves from the gasoline dataset. This is motivated by the Karhunen-Loeve-Expansion {\color{green} link formula}
	 First, the initial curves are expressed in terms of a generated bspline basis, created using 50 knots. These smooth curves are then centred, before performing FPCA. For simplification, we assume that
	$\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$

		$$\tilde{X}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{J} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)$$

		\begin{itemize}
			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ and $\tilde{\xi}_{j} \independent \tilde{\xi}_{k}$ for $j \neq k$
			\item Simplification: the $\xi_{j}$ do not follow a normal
			\item $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
		\end{itemize}

    {\color{blue} I shifted this from theory to over here, as it makes more sense in the simulation part.\\
    Very short summary: take fpc's and eigenvalues, use that the scores are independent from each other. Use the eigenvalues as variances and draw from a multivariate normal with the right varcov matrix (normal just because of convenience... No theoretical reasoning)}

    \subsection{Simulation setup}
	The simulation study follows Reiss and Ogden (2007) as a guideline. Similar to Reiss and Ogden (2007), two different true coefficient functions $f_1(t)$ and $f_2(t)$ were chosen that differ in their smoothness:

	\begin{equation}
    	f_1(t) = 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t) 
    \end{equation}

    \begin{equation}
    	\begin{split}
    		f_2(t) = & 1.5 \exp{\left(\frac{-0.5(t-0.3)^2}{0.02^2}\right)} - 4 \exp{\left(\frac{-0.5(t-0.45)^2}{0.015^2}\right)} \\
    				 & + 8 \exp{\left(\frac{-0.5(t-0.6)^2}{0.02^2}\right)} -  \exp{\left(\frac{-0.5(t-0.8)^2}{0.03^2}\right)}
    	\end{split}
    \end{equation}

		\vspace{0.1cm}
		\begin{figure}
			\centering
			\begin{minipage}{.5\textwidth}
				\centering
  				\includegraphics[width=\textwidth]{Graphics/smooth_function.png}
  				\caption{$f_1(t)$, smooth function}
  				\label{fig:test1}
			\end{minipage}%
			\begin{minipage}{.5\textwidth}
	  			\centering
  				\includegraphics[width=\textwidth]{Graphics/bumpy_function.png}
  				\caption{$f_2(t)$, bumpy function}
  				\label{fig:test2}
			\end{minipage}
		\end{figure}

Two different error-terms $\epsilon $ were created by first generating iid standard normal error and then multiplying them by a error variation $\sigma_e $ which is calculated such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6. The two error-terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$.

$$Y_{1,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)$$

$$Y_{2,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)$$

		where $Z \sim \mathcal{N}(0,1)$ to test the methods with different signal-to-noise ratios. In total we create four combinations for the simulation, using the two true coefficient functions and the two sets of responses. These four combinations are then used with different number of cubic bspline basis-function $(5,6,...,25)$ and fourier functions $(1,2,...,25)$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we use 10f cross-validation. The simulation was done with R (version...). In total we carried out 2000 simulations for each combination of data and number of basis functions. {\color{green} Information about version and link to repo / package in footnote??}

	\subsection{Results}
